% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{cv-style}         

\sethyphenation[variant=british]{english}{}

\usepackage{xcolor}% http://ctan.org/pkg/xcolor
\usepackage{hyperref}% http://ctan.org/pkg/hyperref
\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!red,
  urlcolor=blue!70!black
}
\documentclass{article}
\usepackage{tikz}

\newcommand{\ExternalLink}{%
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{% 
        \begin{scope}[x=1ex, y=1ex]
            \clip (-0.1,-0.1) 
                --++ (-0, 1.2) 
                --++ (0.6, 0) 
                --++ (0, -0.6) 
                --++ (0.6, 0) 
                --++ (0, -1);
            \path[draw, 
                line width = 0.5, 
                rounded corners=0.5] 
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5) 
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1) 
            -- (1, 1) -- (1, 0.6);
        }
    }
\begin{document}

\header{Akash }{Lukhi }           % Your name

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION  -- In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------

\begin{aside}
%
\section{Contact}
A-103 Apple Hevan,
Abc Circle, Mota 
Varachha, Surat
~
Mobile no:
+91 6353001311
~
Email:-
akashlukhi123
@gmail.com
%

\section{Languages}
English, Hindi,
Gujarati(M.T)
%


\section{Links}
Github: \href{https://github.com/akashlukhi}{akashlukhi}
Codechef: \href{https://www.codechef.com/users/akash_lukhi}{akash\_lukhi}
Hackerrank: \href{https://www.hackerrank.com/akashlukhi}{akashlukhi}
Linkedin: \href{https://www.linkedin.com/in/akash-lukhi-b0540a213/}{Akash Lukhi}
%

\section{Programming
   Languages}
{\color{red} $\varheartsuit$} Python
C, JAVA, ASP.NET
Visual Basic C\#,
PHP, MySQL, HTML,
CSS, JavaScript
%

\section{Frameworks}
Django, Flask,
Angular.
%
\section{Learning}
FastAPI

\end{aside}



%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
%------------------------------------------------
\entry
{2018--2022}
{B.Tech {\normalfont in Computer Engineering ( 8.39 CPI )}}
{Dharmsinh Desai University}
{\vspace{-0.3cm}}
%------------------------------------------------
\entry
{2016--2018}
{HSC {\normalfont from Ashadeep Vidhyalaya, Surat ( 87.40 \% )}}
{GHSEB}
{\vspace{-0.3cm}}
\entry
{2015-2016}
{SSC {\normalfont from Mangaldeep Vidhyalaya, Surat ( 86.00 \% )}}
{GSEB}
{}

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	OTHER QUALIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{Projects}

\begin{entrylist}
%------------------------------------------------
\entry
{Apr-2021}
{Speech Processing and Voice Recognition}
{Flask Framework | Python | SQLAlchemy}
{ \textbullet\, Like Google Assistant or Alexa, an online application that may be used as a voice assistant. \newline
 \textbullet\, The user can provide input in the form of a voice command, which the system will process and respond to. Set or remove reminders, play YouTube music, start or close programmes, and so on are some of the capabilities given by this system.}
{\vspace{-0.3cm}}
\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{Apr-2021}
{PagarBook}
{WCF Service | Web API | ASP.net | C\# | MySQL }
{ \textbullet\, We used webapi and wcf services in this Windows forms-based application. Admins can change or add information about employees, and they must update attendance every day.\newline
 \textbullet\, Our software can determine an employee's pay based on their attendance. }
{\vspace{-0.3cm}}

\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{Oct-2020}
{E-Wallet Web Application}
{Angular 7 | Node.js | MongoDB }
{ \textbullet\, A Mean-stack application where users can register and log in. Users can only sign up if they have a bank account in our database.\newline     \textbullet\, Money can be transferred using a user's account number and phone number. \newline
 \textbullet\, Users can also request money to be sent to their phone number, money to be transferred from their bank account to their wallet, pay bills, make reservations, contact us, and use other services.}
{\vspace{-0.3cm}}
\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{Oct-2020}
{E-Commerce Web Application}
{ASP.net | C\# | MySQL }
{ \textbullet\, A web application that allows user to register and login. After login he/she can add a intrested product to cart or favourite list. After adding all intrested products to cart he/she can pay for item and checkout.\newline
 \textbullet\, Admin has functionality to add/update/delete a product and can change a delivery status from undelivered to delivered.}
{\vspace{-0.3cm}}


%------------------------------------------------
\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{Apr-2020}
{Bus Ticket Booking}
{Python | Django Framework and PHP | phpMyDdmin}
{ \textbullet\, A web-based programme, the Online Bus Ticket Reservation System. where the administrator may add or edit bus information, and users can login or register to verify bus availability on their routes and dates.\newline
 \textbullet\, user can make a reservation or cancel it within 24 hours of departure. User can also obtain an e-ticket from our website.}
{\vspace{-0.3cm}}


%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------



\newline

\section{Interests}
  \vspace{-0.2cm}
\begin{entrylist}
%------------------------------------------------

\entry
{}
{Python programming and backend}
{}
{Develop creative application in Python as well backend developments.}

\end{entrylist}\
\begin{entrylist}
%------------------------------------------------
\entry
{}
{Learn about new Web technology}
{}
{Learn about the latest technology which helpful in company and Improve my programming Skills as well.}
\end{entrylist}\

%----------------------------------------------------------------------------------------
%	Achievement  SECTION
%----------------------------------------------------------------------------------------

\clearpage
\section{Achievements}
\begin{entrylist}
%------------------------------------------------
\entry
{}
{Successfully Deployed Web Applications }
{Heroku}
{\href{https://safepay1.herokuapp.com/}{E-Wallet Web Application \ExternalLink} 
\newline
\href{https://bluebusbooking.herokuapp.com/}{Bus-Ticket Booking Web Application \ExternalLink} 
}

%------------------------------------------------
\end{entrylist}
\begin{entrylist}
\entry
{}
{HackerRank Achievments }
{}
{ Got Certified and achieved 5 star in Problem Solving and python.}

%------------------------------------------------
\end{entrylist}
\begin{entrylist}
%------------------------------------------------
\entry
{}
{Codechef}
{}
{Achieved 3 star Rating in Codechef.}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}
  \vspace{-0.2cm}

\begin{entrylist}
%------------------------------------------------

%------------------------------------------------
\entry{}
  {Programming Ability}
{}
{\jobtitle{}Good programming skills in Python, JAVA and C.}
\entry{}
{Knowledge of Git Version Control System}{}
{\jobtitle{}My all project repository are available on Github. }
\entry{}
  {Quick Learning Capability }
  {}
  {\jobtitle{}Quick learning all the fundamental of the Software Technology.}
  \entry
  {}
  {Good in Communication}
  {}
  {\jobtitle{}Know three different languages. }


  
%------------------------------------------------
%------------------------------------------------

\end{entrylist}
\end{document}